### 2022-04-30 draft.tex
Deploying to gh-pages from @ EcoComplex/TrophicResourcesEdaphic@ae4da2bf08734f1e5fa96d51a2ee654e60bd8a39 🚀

Ecosystem sustainable use requires reliable information about its biotic
and abiotic structure and functioning. Accurate knowledge of trophic
relations is central for the understanding of ecosystem dynamics, which
in turn, is essential for food web stability analyzes and the
development of sustainable practices. There is a rapid growth in the
knowledge on how belowground biodiversity regulates the structure and
functioning of terrestrial ecosystems. Although, the available
information about trophic relationships is hard to find and fragmented.
This gathering the information available worldwide about the food
resources of soil mesofauna. From the 3105 hits of the initial search on
food resources of soil microarthropods, only a total of 195 published
works related particular species, genera, and families to particular
trophic resources, the majority of them dealing with soils of the
Palearctic region. From the 195 publications we extracted 3009 records
relating specific taxonomic groups to their trophic resources, 20\%
mention saprophytic fungi as a food resource, 16\% cite microfauna, 11\%
mention bacteria, 10\% litter and 5\% cite Mycorrhizal fungi. The
available information was highly skewed, the 73.71\% comes from Acari,
and within these, 50.62\% correspond just to Sarcoptiformes. For
Collembola, the literature is scarce, the majority coming from
Arthropleona. This review highlights the general lack of information
relating species, genera, and families of the soil mesofauna to specific
trophic resources. It also highlights that available research mostly
comes from European sites, with the use of trophic resources by the
mesofauna of the majority of the soils in other parts of the world still
largely unknown.

@@

Only in the last few decades, sustainable use of the soil has come
sharply into focus. The Ecosystem Millennium Assessment (2005), the
report on Global Biodiversity and Ecosystem Services (IPBES, 2019), and
the recent State of Knowledge of Soil Biodiversity (FAO, 2020) clearly
state the importance of the soil ecosystem and the central role that
soil biodiversity plays on ecosystem services. However, critical
information is lacking on edaphic biodiversity and interaction webs for
most soils.

@@

This review gathers the information currently available regarding the
use of trophic resources by the edaphic microarthropods. This
information, together with other characteristic features~of the soil
microarthropods, will allow building a food web interactions network,
that could result in a better understanding of the structure and
functioning of the edaphic biota (FAO, 2020). Trophic networks will, in
turn, allow for~comparing the state of different soils, or the same
soils under different intensities of anthropic impact (Thompson et al.,
2012).

@@

The first eligibility criterion to reduce the number of records was to
select those papers whose titles or abstracts relate soil
microarthropods to trophic resources (425 titles). From these, we
selected those papers that effectively mention families, genera, or
species of soil mites and springtails, relating them with at least one
trophic resource. This resulted in 195 publications, which can be
consulted in Electronic Supplementary Material I (ESM I). All the
microarthropods recorded in the 195 publications cited can be found in
ESM II, which is cross-referenced with ESM I. A flow diagram of the
bibliography search and selection procedure is also provided as ESM III.

@@

We associate taxa and those resources, so that: a- if the publication
indicated a food item it was assigned to a trophic resource in which it
is defined, b- or if the taxa are grouped in some guild or trophic
category, then each taxon was assigned the typical resources consumed by
that category.

Based on this allocation strategy, we developed a database presented in
Supplementary material II. The taxonomic information and the trophic
resources were obtained from the different sections of the publications
and their appendices (Thakur et al., 2020). In a complementary way, each
taxon found has all the classification levels according to Krantz 2009
and Hopkin 2007, for mites and springtails respectively.

@@

The calculations, graphs, and tables were prepared using Microsoft Excel
and R Statistical software version 4.1.2 (R Core Team 2021).

@@

From the 3105 papers initially recovered with the searches, 195 papers
were found to meet our criteria (see ESM III). A total of 132 articles
from the 195 selected publications (ESM I) mention the countries in
which the studies were carried out. Of these, 1 article belongs to the
Ethiopian region, 3 to the Neotropical region, 3 to the Oriental region,
7 to the Australian region, 34 to the Nearctic region, 74 are all
located in the Palearctic region, and the remaining 10 are from the
Antarctic region. (Figure 1). This is important to highlight because the
species strongly vary depending on the biogeographic region. There are
105 publications mentioning the environments in which the studies were
conducted; from these 58 were temperate forests, 3 tropical forests, 21
grasslands, 23 agroecosystems, and 11 deserts.

@@

We obtained a total of 3009 records about trophic relationships (ESM
II), with Acari contributing with 2218 records (73,71\%), and within
this number, the majority (50.63\%) correspond to Sarcoptiformes. At the
species level, 168 records were Collembola, and 422 records were Acari.
At the genus level, 572 records were found. The family level adds 210
records with 51 different families out of the total of 161 families
identified in this review.

@@

\begin{figure}
\centering
\includegraphics[width=4.92014in,height=4.92014in]{Figures/Metodo_ByTaxLevel.jpeg}
\caption{Methods used in the literature to assign trophic resources to
soil mesofauna taxa. Colors within columns refer to the number of
different taxonomic levels for which each method assigned at least one
resource. Assay: laboratory tests and observations. Isotopes: stable
isotopes. Gut: intestinal content. Enzymes: Digestive enzymes. Mouth:
mouthparts morphology. Lipid: lipid profile. Mo. det: molecular
detection of intestinal content, f.p.: Food preference assays. Obs.:
direct lab observations of feeding activity. Reviews: general reviews by
other authors.}
\end{figure}

@@

Intestinal contents analyses with molecular techniques for the detection
of DNA is a tool of recent development and represent 0.8\% of the total
records.

@@

The main resource mentioned corresponds to saprophytic fungi (19.7\%)
followed by microfauna (15.6\%), bacteria (10.8\%), and litter (10.3\%),
the records for mites, collembola, enchytraeidae, larvae, and eggs
accumulate 725 mentions (24\%) (Table 1). It is worth noting that a
higher number of records have been taken to the species level. For
instance, 592 trophic records are associated with saprophytic fungi
consumption, of which 16 were associated with the taxonomic level of the
family, 105 to the genus level, and 471 to the species level.

\begin{figure}
\centering
\includegraphics[width=5.11667in,height=5.11667in]{Figures/Recursos_ByMetodo.jpeg}
\caption{The number of records in the literature assigning each one of
the 13 trophic resources to a mesofauna taxon as shown in Table 1.
Colors in the columns refer to the method used to assign those trophic
resources to a particular taxon. Methods as in Fig. 2.}
\end{figure}

Laboratory observations (the most used method), mention the use of the
thirteen trophic resources (Figure 3) in which the order of importance
according to the number of mentions is microfauna \textgreater{}
springtails \textgreater{} mites \textgreater{} saprophytic fungi
\textgreater{} invertebrate eggs \textgreater{} enchytraeids
\textgreater{} larvae of invertebrates that accumulate 82.3\%. For this
empirical method, the main resources correspond to typical resources of
predatory animals except for saprophytic fungi, the main taxa mentioned
is Mesostigmata. Figure 3 also shows (in colors) that the most important
methods used for resource assignment, according to the number of
citations in the bibliography, was: direct observations (706 records)
\textgreater{} gut contents (639) \textgreater{} isotopes (591)
\textgreater{} lab assays (503) \textgreater{} enzymes (178)
\textgreater{} feeding preference assays (131 records).

@@

\begin{figure}
\centering
\includegraphics[width=5.4125in,height=3.60833in]{Figures/Bi_Orden_Recurso.jpeg}
\caption{Bipartite graph showing the use of trophic resources by the
main orders of Acari and Collembola. Upper nodes: Acari and Collembola
orders as in Table 2. Lower nodes: trophic resources. The thickness and
intensity of the lines give an idea of the proportion of mentions in the
available literature about their use of trophic resources. Resource
names as in Tables 1 and 2.}
\end{figure}

@@

It is also to be noted that the information available for Acari and
Collembola is strongly asymmetric, corresponding mainly to Acari, order
Sarcoptiformes.

@@

This information must be interpreted with caution, however, because
within a taxonomic category, each species could apply different
strategies to the problem of exploiting resources (Lavelle and Spain,
2001; Moore et al.,1988), as many taxa in the available literature are
considered to be general consumers.

@@

Behan-Pelletier V, Newton G., 1999. Linking soil biodiversity and
ecosystem function. The taxonomic dilemma. BioScience 2.
\href{https://doi.org/10.2307/1313540}{\underline{https://doi.org/10.2307/1313540}}.

Bellinger PF, Christiansen KA, Janssens F., 2020. Internet resource
available from:
\href{http://www.collembola.org/}{\underline{http://www.collembola.org}}.
Last updated: November 30, 2020. Last accessed: December 23, 2020.

Berg, M.P., Stoffer, M., van den Heuvel, H. 2004. Feeding guilds in
Collembola based on digestive enzymes. Pedobiologia 48, 589-601. DOI:
\href{http://dx.doi.org/10.1016\%2Fj.pedobi.2004.07.006}{\underline{\hfill\break
10.1016/j.pedobi.2004.07.006}}

@@

Briones MJI., 2014. Soil fauna and soil functions: a jigsaw puzzle.
Front. Environ. Sci. 2, 1--22. https://doi.org/10.3389/fenvs.2014.00007

@@

Buryn R, Brandl R., 1992. Are the morphometrics of chelicerae correlated
with diet in mesostigmatid mites (Acari)? Exp. Appl. Acarol. 14, 67--82.
\href{https://doi.org/10.1007/BF01205353}{\underline{https://doi.org/10.1007/BF01205353}}

@@

Clark FE., 1971. Bacterios del Suelo, In: Burges, A., Raw, F. (Eds.),
Biología del Suelo, Chapter 2. Ediciones Omega, Barcelona. pp.~27--68.

@@

Hooper DU, Chapin FS, Ewel JJ, Hector A, Inchausti P, Lavorel S, Lawton
JH, Lodge DM, Loreau M, Naeem S, Schmid B, La HS, Symstad AJ, Vandermeer
J, Wardle DA., 2005. Effects of biodiversity on ecosystem functioning: A
consensus of current knowledge. Ecol. Monogr. 75, 33.
\href{https://doi.org/10.1890/04-0922}{\underline{https://doi.org/10.1890/04-0922}}

Hopkin, S. P. (1997).~Biology of the springtails: (Insecta: Collembola).
Oxford University Press. Oxford, UK. 340 pp.

@@

Pey B, Nahmani J, Auclerc A, Capowiez Y, Cluzeau D, Cortet J, Decaëns T,
Deharveng L, Dubs F, Joimel S, Briard C, Grumiaux F, Laporte MA, Pasquet
A, Pelosi C, Pernin C, Ponge JF, Salmon S, Santorufo L, Hedde M., 2014.
Current use of and future needs for soil invertebrate functional traits
in community ecology. Basic Appl. Ecol. 15, 194--206.
\href{https://doi.org/10.1016/j.baae.2014.03.007}{\underline{https://doi.org/10.1016/j.baae.2014.03.007}}.

@@

Pollierer MM, Scheu S, Haubert D., 2010. Taking it to the next level:
Trophic transfer of marker fatty acids from basal resource to predators.
Soil Biol. Biochem. 42, 919--925.
\href{https://doi.org/10.1016/j.soilbio.2010.02.008}{\underline{https://doi.org/10.1016/j.soilbio.2010.02.008}}

@@

Ponge JF., 1991. Food resources and diets of soil animals in a small
area of Scots pine litter. Geoderma. 49, 33--62.
https://doi.org/10.1016/0016-7061(91)90090-G

Potapov AM, Pollierer MM, Salmon S, Šustr V, Chen TW., 2020.
Multidimensional trophic niche approach: gut content, digestive enzymes,
fatty acids, and stable isotopes in Collembola. bioRxiv
2020.05.15.098228.
\href{https://doi.org/10.1101/2020.05.15.098228}{\underline{https://doi.org/10.1101/2020.05.15.098228}}

Potapov AM, Tiunov AV, Scheu S., 2019. Uncovering trophic positions and
food resources of soil animals using bulk natural stable isotope
composition: Stable isotopes in soil food web studies. Biol. Rev.~94,
37--59. \underline{https://doi.org/10.1111/brv.12434}

@@

Schmidt KH., 2020. Internet resource available from:
\href{http://miteresearch.org/}{\underline{http://miteresearch.org}}.
Last accessed: December 23, 2020.

@@

\hypertarget{figures-and-tables}{%
\subsection{Figures and Tables}\label{figures-and-tables}}

\begin{longtable}[]{@{}lcclll@{}}
\caption{Basic description of trophic resources. Total allocations by
trophic resource, absolute values (percentage values). The number of
mentions of a trophic resource for the level of taxonomic resolution.
\textsuperscript{1}Supplementary material II
\textsuperscript{2}Supplementary material I \textsuperscript{a}Berg \&

@@

\begin{minipage}[b]{0.09\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[b]{0.37\columnwidth}\centering

@@

\end{minipage} & \begin{minipage}[b]{0.27\columnwidth}\centering
\textbf{Number of consumer records}\strut
\end{minipage} & \begin{minipage}[b]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[b]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[b]{0.03\columnwidth}\raggedright
\strut

@@

\begin{minipage}[t]{0.09\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.37\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.27\columnwidth}\centering
Total allocations by trophic resource, absolute values (percentage
values)\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\begin{minipage}[t]{0.09\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.37\columnwidth}\centering

@@

\end{minipage} & \begin{minipage}[t]{0.27\columnwidth}\centering
\textbf{592 (19,7)}\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\textbf{471}\strut

@@

\begin{minipage}[t]{0.09\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.27\columnwidth}\centering

@@

\end{minipage} & \begin{minipage}[t]{0.27\columnwidth}\centering
\textbf{149 (4,9)}\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\textbf{124}\strut

@@

\textbf{\underline{Supplementary Material Captions}}

>>>>

Ecosystem sustainable use requires reliable information about its biotic
and abiotic structure and functioning. Accurate knowledge of trophic
relations is central for the understanding of ecosystem dynamics, which
in turn, is essential for food web stability analyzes and the
development of sustainable practices. There is a rapid growth in the
knowledge on how belowground biodiversity regulates the structure and
functioning of terrestrial ecosystems. Although, the available
information about trophic relationships is hard to find and fragmented.
This gathering the information available worldwide about the food
resources of soil mesofauna. From the 3105 hits of the initial search on
food resources of soil microarthropods, only a total of 196 published
works related particular species, genera, and families to particular
trophic resources, the majority of them dealing with soils of the
Palearctic region. From the 196 publications we extracted 3009 records
relating specific taxonomic groups to their trophic resources, 20\%
mention saprophytic fungi as a food resource, 16\% cite microfauna, 11\%
mention bacteria, 10\% litter and 5\% cite Mycorrhizal fungi. The
available information was highly skewed, the 73.71\% comes from Acari,
and within these, 50.62\% correspond just to Sarcoptiformes. For
Collembola, the literature is scarce, the majority coming from
Arthropleona. This review highlights the general lack of information
relating species, genera, and families of the soil mesofauna to specific
trophic resources. It also highlights that available research mostly
comes from European sites, with the use of trophic resources by the
mesofauna of the majority of the soils in other parts of the world still
largely unknown.

@@

Only in the last few decades, sustainable use of the soil has come
sharply into focus. The report on Global Biodiversity and Ecosystem
Services (IPBES, 2019), and the recent State of Knowledge of Soil
Biodiversity (FAO, 2020) clearly state the importance of the soil
ecosystem and the central role that soil biodiversity plays on ecosystem
services. However, critical information is lacking on edaphic
biodiversity and interaction webs for most soils.

@@

This review gathers the information currently available regarding the
use of trophic resources by the edaphic microarthropods. This
information, together with other characteristic features of the soil
microarthropods, will allow building a food web interactions network,
that could result in a better understanding of the structure and
functioning of the edaphic biota (FAO, 2020). Trophic networks will, in
turn, allow for comparing the state of different soils, or the same
soils under different intensities of anthropic impact (Thompson et al.,
2012).

@@

The first eligibility criterion to reduce the number of records was to
select those papers whose titles or abstracts relate soil
microarthropods to trophic resources (425 titles). From these, we
selected those papers that effectively mention families, genera, or
species of soil mites and springtails, relating them with at least one
trophic resource. This resulted in 196 publications, which can be
consulted in Electronic Supplementary Material I (ESM I). All the
microarthropods recorded in the 196 publications cited can be found in
ESM II, which is cross-referenced with ESM I. A flow diagram of the
bibliography search and selection procedure is also provided as ESM III.

@@

We associate taxa and those resources, so that: a) if the publication
indicated a food item it was assigned to a trophic resource in which it
is defined, b) or if the taxa are grouped in some guild or trophic
category, then each taxon was assigned the typical resources consumed by
that category.

Based on this allocation strategy, we developed a database presented in
Supplementary material II. The taxonomic information and the trophic
resources were obtained from the different sections of the publications
and their appendices (Thakur et al., 2020). In a complementary way, each
taxon found has all the classification levels according to Krantz 2009
and Hopkin 2007, for mites and springtails respectively. The database is
also available in the github repository
\url{https://github.com/EcoComplex/TrophicResources} and Zenodo
\url{https://zenodo.org/record/XXXXXXX}.

@@

The calculations, graphs, and tables were prepared using Microsoft Excel
and R Statistical software version 4.1.2 (R Core Team 2021), the source
code is available at Github
\url{https://github.com/EcoComplex/TrophicResources} and Zenodo
\url{https://zenodo.org/record/XXXXXXX}..

@@

From the 3105 papers initially recovered with the searches, 196 papers
were found to meet our criteria (see ESM III). A total of 133 articles
from the 196 selected publications (ESM I) mention the countries in
which the studies were carried out. Of these, 1 article belongs to the
Ethiopian region, 3 to the Neotropical region, 3 to the Oriental region,
7 to the Australian region, 34 to the Nearctic region, 75 are all
located in the Palearctic region, and the remaining 10 are from the
Antarctic region. (Figure 1). This is important to highlight because the
species strongly vary depending on the biogeographic region. There are
106 publications mentioning the environments in which the studies were
conducted; from these 59 were temperate forests, 3 tropical forests, 21
grasslands, 23 agroecosystems, and 11 deserts.

@@

We obtained a total of 3015 records on trophic relationships (ESM II),
with Acari contributing 2218 records (73.57\%), and within this number,
the majority (50.86\%) corresponds to Sarcoptiformes. According to the
taxonomic resolution, data of 170 species, 30 genera and 2 families of
Collembola and 412 species, 131 genera and 49 families of Acari were
obtained.

@@

\begin{figure}
\centering
\includegraphics[width=4.92014in,height=4.92014in]{Figures/Metodo_ByTaxLevel.png}
\caption{Methods used in the literature to assign trophic resources to
soil mesofauna taxa. Colors within columns refer to the number of
different taxonomic levels for which each method assigned at least one
resource. Assay: laboratory tests and observations. Isotopes: stable
isotopes. Gut: intestinal content. Enzymes: Digestive enzymes. Mouth:
mouthparts morphology. Lipid: lipid profile. Mo. det: molecular
detection of intestinal content, f.p.: Food preference assays. Obs.:
direct lab observations of feeding activity. Reviews: general reviews by
other authors.}
\end{figure}

@@

Intestinal contents analyses with molecular techniques for the detection
of DNA is a tool of recent development and represent 2\% of the total
records.

@@

The main resource mentioned corresponds to saprophytic fungi (19.7\%)
followed by microfauna (15.6\%), bacteria (10.8\%), and litter (10.3\%),
the records for mites, collembola, enchytraeidae, larvae, and eggs
accumulate 725 mentions (24\%) (Table 1). It is worth noting that a
higher number of records have been taken to the species level. For
instance, 592 trophic records are associated with saprophytic fungi
consumption, of which 16 were associated with the taxonomic level of the
family, 105 to the genus level, and 474 to the species level.

\begin{figure}
\centering
\includegraphics[width=5.11667in,height=5.11667in]{Figures/Recursos_ByMetodo.png}
\caption{The number of records in the literature assigning each one of
the 13 trophic resources to a mesofauna taxon as shown in Table 1.
Colors in the columns refer to the method used to assign those trophic
resources to a particular taxon. Methods as in Fig. 2.}
\end{figure}

Laboratory observations (the most used method), mention the use of the
thirteen trophic resources (Figure 3) in which the order of importance
according to the number of mentions is microfauna \textgreater{}
springtails \textgreater{} mites \textgreater{} saprophytic fungi
\textgreater{} invertebrate eggs \textgreater{} enchytraeids
\textgreater{} larvae of invertebrates that accumulate 82.3\%. For this
empirical method, the main resources correspond to typical resources of
predatory animals except for saprophytic fungi, the main taxa mentioned
is Mesostigmata. The stacked bars (Figure 3) show the different
proportions in which the methods provide evidence of the use of a
resource, if the contribution of each method is considered according to
the number of citations in the bibliography, they are counted in
decreasing order: direct observations (706 records) \textgreater{}
intestinal content (639) \textgreater{} isotopes (591) \textgreater{}
laboratory tests (503) \textgreater{} enzymes (178) \textgreater{} food
preference tests (131 records).

@@

\begin{figure}
\centering
\includegraphics[width=5.4125in,height=3.60833in]{Figures/Bi_Orden_Recurso.png}
\caption{Bipartite graph showing the use of trophic resources by the
main orders of Acari and Collembola. Upper nodes: Acari and Collembola
orders as in Table 2. Lower nodes: trophic resources. The thickness and
intensity of the lines give an idea of the proportion of mentions in the
available literature about their use of trophic resources. Resource
names as in Tables 1 and 2.}
\end{figure}

@@

It is also to be noted that the information available for Acari and
Collembola is strongly asymmetric, corresponding mainly to the order
Sarcoptiformes in Acari and to Arthropleona in Collembola.

@@

However, this information must be interpreted with caution, because
within a taxonomic category each species could apply different
strategies when exploiting food resources (Lavelle and Spain, 2001;
Moore et al., 1988), although the taxa treated here are considered
generalist consumers, recently the term ``choosy generalist'' was
suggested as the behavior that characterizes consumers that inhabit
soils (Potapov et al.~2022)

@@

Behan-Pelletier V, Newton G., 1999. Linking soil biodiversity and
ecosystem function. The taxonomic dilemma. BioScience 2.
\href{https://doi.org/10.2307/1313540}{{[}https://doi.org/10.2307/1313540{]}}.

Bellinger PF, Christiansen KA, Janssens F., 2020. Internet resource
available from:
\href{http://www.collembola.org/}{{[}http://www.collembola.org{]}}. Last
updated: November 30, 2020. Last accessed: December 23, 2020.

Berg, M.P., Stoffer, M., van den Heuvel, H. 2004. Feeding guilds in
Collembola based on digestive enzymes. Pedobiologia 48, 589-601. DOI:
\href{http://dx.doi.org/10.1016\%2Fj.pedobi.2004.07.006}{{[}\textbackslash10.1016/j.pedobi.2004.07.006{]}}

@@

Briones MJI., 2014. Soil fauna and soil functions: a jigsaw puzzle.
Front. Environ. Sci. 2, 1--22.
\url{https://doi.org/10.3389/fenvs.2014.00007}

@@

Buryn R, Brandl R., 1992. Are the morphometrics of chelicerae correlated
with diet in mesostigmatid mites (Acari)? Exp. Appl. Acarol. 14, 67--82.
\href{https://doi.org/10.1007/BF01205353}{{[}https://doi.org/10.1007/BF01205353{]}}

@@

Clark FE., 1971. Bacterias del Suelo, In: Burges, A., Raw, F. (Eds.),
Biología del Suelo, Chapter 2. Ediciones Omega, Barcelona. pp.~27--68.

@@

Hooper DU, Chapin FS, Ewel JJ, Hector A, Inchausti P, Lavorel S, Lawton
JH, Lodge DM, Loreau M, Naeem S, Schmid B, La HS, Symstad AJ, Vandermeer
J, Wardle DA., 2005. Effects of biodiversity on ecosystem functioning: A
consensus of current knowledge. Ecol. Monogr. 75, 33.
\href{https://doi.org/10.1890/04-0922}{{[}https://doi.org/10.1890/04-0922{]}}

Hopkin, S. P. (1997). Biology of the springtails: (Insecta: Collembola).
Oxford University Press. Oxford, UK. 340 pp.

@@

Pey B, Nahmani J, Auclerc A, Capowiez Y, Cluzeau D, Cortet J, Decaëns T,
Deharveng L, Dubs F, Joimel S, Briard C, Grumiaux F, Laporte MA, Pasquet
A, Pelosi C, Pernin C, Ponge JF, Salmon S, Santorufo L, Hedde M., 2014.
Current use of and future needs for soil invertebrate functional traits
in community ecology. Basic Appl. Ecol. 15, 194--206.
\href{https://doi.org/10.1016/j.baae.2014.03.007}{{[}https://doi.org/10.1016/j.baae.2014.03.007{]}}.

@@

Pollierer MM, Scheu S, Haubert D., 2010. Taking it to the next level:
Trophic transfer of marker fatty acids from basal resource to predators.
Soil Biol. Biochem. 42, 919--925.
\href{https://doi.org/10.1016/j.soilbio.2010.02.008}{{[}https://doi.org/10.1016/j.soilbio.2010.02.008{]}}

@@

Ponge JF., 1991. Food resources and diets of soil animals in a small
area of Scots pine litter. Geoderma. 49, 33--62.
\url{https://doi.org/10.1016/0016-7061(91)90090-G}

Potapov AM, Beaulieu F, Birrkhofer K, Bluhm SL, Degtyarev MI, Devetter
M, Goncharov AA, Gongalsky KB, Klarner B, Korobushkin DI, Liebke DF,
Maraun M, Mc Donnell RJ, Pollierer MM, Schaefer I, Shrubovych J,
Semenyuk I I, Sendra A, Tuma J, Tůmová M, Vassilieva AB, Chen T, Geisen
S, Schmidt O, Tiunov AV, Scheu S. 2022. Feeding habits and
multifunctional classification of soil-associated consumers from
protists to vertebrates. Biological Reviews
\url{https://doi.org/10.1111/brv.12832}

Potapov AM, Pollierer MM, Salmon S, Šustr V, Chen TW., 2020.
Multidimensional trophic niche approach: gut content, digestive enzymes,
fatty acids, and stable isotopes in Collembola. bioRxiv
2020.05.15.098228.
\href{https://doi.org/10.1101/2020.05.15.098228}{{[}https://doi.org/10.1101/2020.05.15.098228{]}}

Potapov AM, Tiunov AV, Scheu S., 2019. Uncovering trophic positions and
food resources of soil animals using bulk natural stable isotope
composition: Stable isotopes in soil food web studies. Biol. Rev.~94,
37--59. {[}https://doi.org/10.1111/brv.12434{]}

@@

Schmidt KH., 2020. Internet resource available from:
\href{http://miteresearch.org/}{{[}http://miteresearch.org{]}}. Last
accessed: December 23, 2020.

@@

\hypertarget{tables}{%
\subsection{Tables}\label{tables}}

\begin{longtable}[]{@{}lccccc@{}}
\caption{Basic description of trophic resources. Total records of
consumers by trophic resource with absolute values and percentages; and
the number of records by taxonomic resolution.\textsuperscript{a}Berg \&

@@

\begin{minipage}[b]{0.11\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[b]{0.45\columnwidth}\centering

@@

\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\centering
\textbf{Total consumer records (\%)}\strut
\end{minipage} & \begin{minipage}[b]{0.04\columnwidth}\centering
\end{minipage} & \begin{minipage}[b]{0.04\columnwidth}\centering
\end{minipage} & \begin{minipage}[b]{0.04\columnwidth}\centering

@@

\begin{minipage}[t]{0.11\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.45\columnwidth}\centering

@@

\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
\textbf{595 (19,7)}\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\centering

@@

\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\centering

@@

\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\centering
\textbf{474}\strut

@@

\begin{minipage}[t]{0.11\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering

@@

\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\centering
\textbf{152 (4,9)}\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\centering

@@

\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\centering
\textbf{127}\strut

@@

\textbf{{[}Supplementary Material Captions{]}}
